% ~1 page total.

% Specify overall aim and objectives and report structure.

\chapter{Introduction}\label{intro}

Traditional drawing techniques such as pen-and-ink have the power to communicate complex form, using only limited colour and a parsimony of ink.
These techniques appear to have fallen out of favour with the advent of computer-generated renderings and the ability to produce photo-realistic graphics.
Despite this, traditional techniques continue to have value, especially for communication of abstract ideas.
Implementations of such techniques in commonly available and free to use computer graphics applications are few and far between, despite a rich body of research being available in the field of Non-Photorealistic Rendering (NPR).

To address this problem, a project has been undertaken to extend a commonly available 3D modelling platform, Blender, by developing an add-on (plug-in) written in Python. The aim of the project is to allow the user to automatically produce high-quality renders of traditional, hand-drawn appearance, through application of monochrome drawing techniques.

The structure of this report is as follows:

\begin{itemize}
	\item{Analysis \& Requirements: The background to the problem is explored and requirements are defined.}
	\item{Design \& Implementation: An overview of the final system design is presented, and implementation challenges discussed.}
	\item{Testing \& Evaluation: Insight is provided into the rationale for system testing and evaluation, and results presented in an effort to measure the success of the implemented system.}
	\item{Appendices: Supplemental material is provided in detail to support the discussions presented in the main body of the report.}
\end{itemize}

An online repository containing all project code, and a detailed development wiki is available on GitHub\footnote{\url{https://github.com/cjbel/blender-hand-drawn-npr}}.